### 2012-09-18 doc/prelim/document/chapters/linear_problem/linear_problem.tex
linear problem updates

\subsubsection{Parallel Matrix-Vector Multiplications}
\label{subsubsec:parallel_mat_vec_mutliply}
We finally consider parallel matrix-vector multiplication operations
using sparse matrices in a compressed storage format. For these
operations, more complex communication patterns will be required given
that the entire global vector is required in order to compute a single
element of the local product vector. Fortunately, the vast majority of
the global vector components will be multiplied by zero due to the
sparse matrix and therefore much of the vector can be
neglected. Instead we only require data from a handful of other
processes.

\begin{figure}[htpb!]
  \begin{center}
    \scalebox{1.5}{
      \input{chapters/linear_problem/partitioned_matrix.pdftex_t} }
  \end{center}
  \caption{Partitioned linear problem.}
  \label{fig:partitioned_linear_problem}
\end{figure}

>>>>

\subsubsection{Parallel Matrix-Vector Multiplications}
\label{subsubsec:parallel_mat_vec_mutliply}
We finally consider parallel matrix-vector multiplication operations
using sparse matrices in a compressed storage format. For these
operations, more complex communication patterns will be required given
that the entire global vector is required in order to compute a single
element of the local product vector. Fortunately, the vast majority of
the global vector components will be multiplied by zero due to the
sparse matrix and therefore much of the vector can be
neglected. Instead we only require data from a handful of other
processes. Consider the sparse matrix-vector multiply in
Figure~\ref{fig:partitioned_matvec_multiply} that is partitioned on 3
processors. 
\begin{figure}[htpb!]
  \begin{center}
    \scalebox{1.5}{
      \input{chapters/linear_problem/partitioned_matrix.pdftex_t} }
  \end{center}
  \caption{Sparse matrix-vector multiply partitioned on 3 processors.}
  \label{fig:partitioned_matvec_multiply}
\end{figure}
Each process owns a set of equations that correlate to the physical
domain of which it has ownership. We can break down the equations
owned by each process in order to devise an efficient scheme for the
mulitplication. Consider the portion of the matrix-vector multiply
problem owned by process 1 in
Figure~\ref{fig:partitioned_mat_vec_multiply}. As shown in
Figure~\ref{fig:mat_vec_proc_1}, the components of the matrix will be
multiplied by pieces of the vector that are owned by all
processors. For those pieces of the matrix that are owned by process
1, we do these multiplications first as no communication is
required. Next, process one gathers the components of the global
vector that it requires to complete its part of the vector
product. Conversely, processes 2 and 3 must scatter their vector
components that are required by other processes (such as process 1) in
order to complete their pieces of the product. This then implies that
these domain connections for proper gather and scatter combinations
must be constructed a priori. These data structures are typically
generated by the partitioning software.
